R Notebook

### 2020-11-24 FEM_R/model_analysis.Rmd
Generated a table with Reactable package including sticky columns and some row styling. This will be the template for all T-test tables soon, just need to add colour gradients and maybe some box plots

require(tidyverse)
require(formattable)
#require(haven)
#require(reshape2)
#require(ggplot2)
#require(gridExtra)

@@

# Specify a function to rename the dataframes, so we can run in an sapply()
rename_first_var <- function(testCSV, prefix) {
  testCSV[,1] <- paste0(testCSV[,1], '_', prefix)
  return(testCSV)
}

@@

# Collect in a list to run a list apply
min_list <- list(min_uw, min_demog, min_binhlth, min_binecon, min_risk)
# Add prefix 'min_' onto every variable name for clarity
min_list <- lapply(min_list, rename_first_var, prefix='min')

@@

```{r}
# names for T-tests directory and filename stem
CV1 <- "ELSA_CrossValidation1/T-tests/"
stem <- "CV1_all_waves_"
# Read in files
cv_uw <- read.csv(paste0(CV1, stem, "unweighted.csv"))
cv_demog <- read.csv(paste0(CV1, stem, "demog.csv"))
cv_binhlth <- read.csv(paste0(CV1, stem, "binhlth.csv"))
cv_binecon <- read.csv(paste0(CV1, stem, "binecon.csv"))
cv_risk <- read.csv(paste0(CV1, stem, "risk.csv"))
# Now collect into list and rename vars for clarity
cv_list <- list(cv_uw, cv_demog, cv_binhlth, cv_binecon, cv_risk)
cv_list <- lapply(cv_list, rename_first_var, prefix='CV')
```

@@

```{r include=FALSE}
# Set up vector with all p-value column names. Require these for table formatting
pValNames <- c('p_value_wave3', 'p_value_wave4', 'p_value_wave5', 'p_value_wave6', 'p_value_wave7', 'p_value_wave8')
```

### Unweighted (died)
```{r echo = FALSE, results = 'asis'}
# Row bind to collect both dfs together
uw <- rbind(min_list[[1]], cv_list[[1]])
# Reorder rows in alphabetical order. This ensures that like variables are clumped together
uw <- arrange(uw, variable)
#uw
formattable(uw, 
            align = c('l', rep('r', ncol(uw) - 1)),
            list(area(col=pValNames) 
                  ~ proportion_bar(color='green', 0.01)))
```
### Demographics
```{r echo = FALSE, results = 'asis'}
# Row bind to collect both dfs together
demog <- rbind(min_list[[2]], cv_list[[2]])
# Reorder rows in alphabetical order. This ensures that like variables are clumped together
demog <- arrange(demog, variable)
formattable(demog, 
            align = c('l', rep('r', ncol(demog) - 1)),
            list(area(col=pValNames) 
                  ~ proportion_bar(color='green', 0.01)))
```
### Binary Health
```{r echo = FALSE, results = 'asis'}
# Row bind to collect both dfs together
binhlth <- rbind(min_list[[3]], cv_list[[3]])
# Reorder rows in alphabetical order. This ensures that like variables are clumped together
binhlth <- arrange(binhlth, variable)
formattable(binhlth, 
            align = c('l', rep('r', ncol(binhlth) - 1)),
            list(area(col=pValNames) 
                  ~ proportion_bar(color='green', 0.01)))
```
### Binary Economic
```{r echo = FALSE, results = 'asis'}
# Row bind to collect both dfs together
binecon <- rbind(min_list[[4]], cv_list[[4]])
# Reorder rows in alphabetical order. This ensures that like variables are clumped together
binecon <- arrange(binecon, variable)
formattable(binecon, 
            align = c('l', rep('r', ncol(binecon) - 1)),
            list(area(col=pValNames) 
                  ~ proportion_bar(color='green', 0.01)))
```
### Risk Behaviours
```{r echo = FALSE, results = 'asis'}
# Row bind to collect both dfs together
risk <- rbind(min_list[[5]], cv_list[[5]])
# Reorder rows in alphabetical order. This ensures that like variables are clumped together
risk <- arrange(risk, variable)
formattable(risk, 
            align = c('l', rep('r', ncol(risk) - 1)),
            list(area(col=pValNames) 
                  ~ proportion_bar(color='green', 0.01)))
```

```{r echo = FALSE, results = 'asis'}
# Row bind to collect both dfs together
risk <- rbind(min_list[[5]], cv_list[[5]])
# Reorder rows in alphabetical order. This ensures that like variables are clumped together
risk <- arrange(risk, variable)
formattable(risk, 
            align = c('l', rep('r', ncol(risk) - 1)),
            list(area(col=pValNames) ~ color_tile('transparent', 'red')))
```

>>>>

require(tidyverse)
require(formattable)
require(reactable)
#require(haven)
#require(reshape2)
#require(ggplot2)
#require(gridExtra)

@@

# Need this code block for reactable tables to be rendered properly in HTML
# Fix from here: https://www.gitmemory.com/issue/glin/reactable/43/618802061
htmltools::tagList(
  reactR::html_dependency_react(),
  reactR::html_dependency_reacttools(),
  reactable::reactable(iris)
)

# function to rename the dataframes, so we can run in an sapply()
rename_first_var <- function(testCSV, prefix) {
  testCSV[,1] <- paste0(testCSV[,1], '_', prefix)
  return(testCSV)
}

# function for shortening column names
shorten_columns <- function(testCSV) {
  testCSV <- testCSV %>%
                rename_at(vars(starts_with('fem_mean_wave')), funs(sub('fem_mean_wave', 'FEM_', .))) %>%
                rename_at(vars(starts_with('elsa_mean_wave')), funs(sub('elsa_mean_wave', 'ELSA_', .))) %>%
                rename_at(vars(starts_with('p_value_wave')), funs(sub('p_value_wave', 'P_Value_', .))) %>%
                rename('Variable' = variable)
}

@@

# Collect in a list to do some formatting
min_list <- list(min_uw, min_demog, min_binhlth, min_binecon, min_risk)
# Add prefix 'min_' onto every variable name for clarity
min_list <- lapply(min_list, rename_first_var, prefix='min')
# Rename columns to be more succinct
min_list <- lapply(min_list, shorten_columns)

@@

```{r}
# names for T-tests directory and filename stem
CV1 <- "ELSA_CrossValidation1/T-tests/"
stem <- "CV1_all_waves_"
# Read in files
cv_uw <- read.csv(paste0(CV1, stem, "unweighted.csv"))
cv_demog <- read.csv(paste0(CV1, stem, "demog.csv"))
cv_binhlth <- read.csv(paste0(CV1, stem, "binhlth.csv"))
cv_binecon <- read.csv(paste0(CV1, stem, "binecon.csv"))
cv_risk <- read.csv(paste0(CV1, stem, "risk.csv"))
# Now collect into list and rename vars and cols for clarity
cv_list <- list(cv_uw, cv_demog, cv_binhlth, cv_binecon, cv_risk)
cv_list <- lapply(cv_list, rename_first_var, prefix='CV')
cv_list <- lapply(cv_list, shorten_columns)
```

@@

```{r include=FALSE}
# Set up vector with all p-value column names. Require these for table formatting
pValNames <- c('P_Value_3', 'P_Value_4', 'P_Value_5', 'P_Value_6', 'P_Value_7', 'P_Value_8')
```

### Unweighted (died)
```{r echo = FALSE, results = 'asis'}
# Row bind to collect both dfs together
uw <- rbind(min_list[[1]], cv_list[[1]])
# Reorder rows in alphabetical order. This ensures that like variables are clumped together
uw <- arrange(uw, Variable)
#uw
formattable(uw, 
            align = c('l', rep('r', ncol(uw) - 1)),
            list(area(col=pValNames) 
                  ~ proportion_bar(color='green', 0.01)))
```
### Demographics
```{r echo = FALSE, results = 'asis'}
# Row bind to collect both dfs together
demog <- rbind(min_list[[2]], cv_list[[2]])
# Reorder rows in alphabetical order. This ensures that like variables are clumped together
demog <- arrange(demog, Variable)
formattable(demog, 
            align = c('l', rep('r', ncol(demog) - 1)),
            list(area(col=pValNames) 
                  ~ proportion_bar(color='green', 0.01)))
```
### Binary Health
```{r echo = FALSE, results = 'asis'}
# Row bind to collect both dfs together
binhlth <- rbind(min_list[[3]], cv_list[[3]])
# Reorder rows in alphabetical order. This ensures that like variables are clumped together
binhlth <- arrange(binhlth, Variable)
formattable(binhlth, 
            align = c('l', rep('r', ncol(binhlth) - 1)),
            list(area(col=pValNames) 
                  ~ proportion_bar(color='green', 0.01)))
```
### Binary Economic
```{r echo = FALSE, results = 'asis'}
# Row bind to collect both dfs together
binecon <- rbind(min_list[[4]], cv_list[[4]])
# Reorder rows in alphabetical order. This ensures that like variables are clumped together
binecon <- arrange(binecon, Variable)
formattable(binecon, 
            align = c('l', rep('r', ncol(binecon) - 1)),
            list(area(col=pValNames) 
                  ~ proportion_bar(color='green', 0.01)))
```
### Risk Behaviours
```{r echo = FALSE, results = 'asis'}
# Row bind to collect both dfs together
risk <- rbind(min_list[[5]], cv_list[[5]])
# Reorder rows in alphabetical order. This ensures that like variables are clumped together
risk <- arrange(risk, Variable)
formattable(risk, 
            align = c('l', rep('r', ncol(risk) - 1)),
            list(area(col=pValNames) 
                  ~ proportion_bar(color='green', 0.01)))
```

```{r echo = FALSE, results = 'asis'}
# Row bind to collect both dfs together
risk <- rbind(min_list[[5]], cv_list[[5]])
# Reorder rows in alphabetical order. This ensures that like variables are clumped together
risk <- arrange(risk, Variable)
formattable(risk, 
            align = c('l', rep('r', ncol(risk) - 1)),
            list(area(col=pValNames) ~ color_tile('transparent', 'red')))
```

# Reactable Package

```{r}

stickyStyle <- list(position = "sticky", left = 0, background = "#fff", zIndex = 1,
                    borderRight = "1px solid #eee")

reactable(risk,
          defaultColDef = colDef(
            header = function(value) gsub('_', ' ', value, fixed=TRUE),
            cell = function(value) format(value, nsmall = 2),
            align='center',
            headerStyle = list(background = "#f7f7f8")
          ),
          columns = list(
            Variable = colDef(minWidth = 160,
                              style = stickyStyle,
                              headerStyle = stickyStyle)
          ),
          bordered = TRUE,
          highlight = TRUE,
          striped = TRUE)
